### 2014-07-17 ResearchNotes.Rmd
Data loaded in.

Research Notes
========================================================
Just a frame right now.

Load data is from http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-data.aspx
Forecasts are from 
http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-forecasts.aspx

```{r}
GoogleSearch<-read.csv("report.csv")
Loads<-read.csv("Loads.csv")
Forecasts<-read.csv("Forecasts.csv")
```

### 2014-07-17 ResearchNotes.Rmd
Editing and formating done.  On to purging forecasts of what I don't need.

@@
 ```
+
+Format the Loads data.
+
+```{r}
+summary(Loads)
+```
+Those just look like column numbers.  I want hour 19, X.20 and the date.
+
+```{r}
+KeyLoads<-Loads[,c(1, 20)]
+names(KeyLoads)<-c("Date","Hour19")
+#convert to numeric
+KeyLoads$Hour19<-as.numeric(as.character(KeyLoads$Hour19))
+
+#convert to ct Date
+KeyLoads$Date<-as.POSIXct(KeyLoads$Date,format='%m/%d/%Y')
+summary(KeyLoads)
+#clean up loads
+rm(Loads)
+```
+
+Clean up forecasts
+
+```{r}
+KeyForecasts<-Forecasts[,c(1,2,21)]
+names(KeyForecasts)<-c("EvalTime","Date","Forecast")
+
+#Fixing time
+KeyForecasts$Date<-as.POSIXct(KeyForecasts$Date,format='%m/%d/%Y')
+KeyForecasts$EvalTime<-as.POSIXlt(KeyForecasts$EvalTime,format="%m/%d/%Y %H:%M:%S")
+summary(KeyForecasts)
+#why are there two of each date?  Because they do day ahead and two day ahead.
+```
+
+Edit the forecasts so that we have only the earliest day ahead forecast.
+
+```{r}
+
+```

### 2014-07-17 ResearchNotes.Rmd
Editing mostly done.  Just doing the  merges on the three data sets.

@@
 ```{r}
+#Keep only the 5am forecasts
+KeyForecasts<-KeyForecasts[as.POSIXlt(KeyForecasts$EvalTime,format="%m/%d/%Y %H:%M:%S")$hour==5,]
+
+#Keep only day ahead
+KeyForecasts<-KeyForecasts[(as.POSIXct(KeyForecasts$EvalTime,format="%m/%d/%Y %H:%M:%S") -as.POSIXct(KeyForecasts$Date,format='%m/%d/%Y'))<0,]
+summary(KeyForecasts)
 
 ```
+
+Now work on the GoogleSearch terms.  This is only for Pennsylvania.
+
+```{r}
+summary(GoogleSearch)
+
+```
+Date is actually ISO.  Hope that does not cause a problem.
+
+Merging the three sets.
+Just to be clear I need the acutal, forecast from day before and search result from two days before.
+That is what I am testing, if I can improve the next day forecast with previous day searches.
+Lots of fun date matching ahead.

### 2014-07-17 ResearchNotes.Rmd
Ran at one point.  It gettting stuck on the sql pull to RTO.  Don't know why it can't find the data.frame.

@@
 Lots of fun date matching ahead.
+
+```{r}
+summary(KeyForecasts)
+summary(KeyLoads)
+library(sqldf)
+
+#Join the two parts form the RTO
+KeyForecasts$Day<-KeyForecasts$Date
+KeyLoads$Day<-KeyLoads$Date
+
+RTO<-sqldf("select KeyForecasts.Day, Forecast, Hour19 from KeyForecasts, KeyLoads where KeyForecasts.Day=KeyLoads.Day;")
+
+GoogleSearch$NextDay<-as.POSIXct(GoogleSearch$Day)+24*60*60
+
+Joint<-sqldf("select RTO.*, GoogleSearch.* from RTO, GoogleSearch where NextDay=Date;")
+#fix the forecast again
+Joint$Hour19<-as.numeric(as.character(Joint$Hour19))
+
+```
+Yes, not a lot of overlap.  Can only do last 30 days with trends for daily.
+
+```{r}
+summary(Joint)
+summary(lm(Hour19~Forecast+Past_30_days,data=Joint))
+```
+Looks like it is significant!
+
+```{r}
+WO<-lm(Hour19~Forecast,data=Joint)
+With<-lm(Hour19~Forecast+Past_30_days,data=Joint)
+
+anova(WO,With)
+```
+
+check the change in SE
+
+```{r}
+summary(WO)$sigma
+summary(With)$sigma
+
+#percent decrease in SE is
+(summary(WO)$sigma-summary(With)$sigma)/summary(WO)$sigma
+```
+
+Nice! 14% reduction in se.  Proof of concept.

### 2014-07-23 ResearchNotes/GoogleTrendLinks.Rmd
Grabed the trends data for 90 days and restructured directory.

Google Trend Links
========================================================
These will get google trends for most of the stats in the PJM teritory.

http://www.google.com/trends/explore#q=weather&geo=US-DE&date=today%203-m&cmpt=date
http://www.google.com/trends/explore#q=weather&geo=US-KY&date=today%203-m&cmpt=date
http://www.google.com/trends/explore#q=weather&geo=US-MD&date=today%203-m&cmpt=date
http://www.google.com/trends/explore#q=weather&geo=US-NJ&date=today%203-m&cmpt=date
http://www.google.com/trends/explore#q=weather&geo=US-OH&date=today%203-m&cmpt=date
http://www.google.com/trends/explore#q=weather&geo=US-PA&date=today%203-m&cmpt=date
http://www.google.com/trends/explore#q=weather&geo=US-VA&date=today%203-m&cmpt=date
http://www.google.com/trends/explore#q=weather&geo=US-WV&date=today%203-m&cmpt=date

### 2014-07-24 DataManipulation/DataManipulation.Rmd
About to merge datasets.

---
title: "DataCleaning"
author: "James Woods"
date: "07/24/2014"
output: html_document
---
Load in the Trends data.
```{r}

library(stringr)
ReadTrends<-function(fileName){
  path<-paste("~/Research/Forecast-Peak-With-Google-Trends/TrendsData/",fileName,sep='')
  file<-read.csv(path)
  names(file)<-c("Date",str_sub(fileName,1, str_length(fileName)-4))
  as.POSIXct(file$Date)
  file
}

#Get the names of the trend files
TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData")

#all the trends in one data frame
AllTrends<-as.data.frame(lapply(TrendsFiles,FUN=ReadTrends))

#Kill the "Date.*" columnns that are duplicates of Date.  Assuming here that the dates all line up
JustTrends<-AllTrends[,c(1,2,seq(from=4,to=length(names(AllTrends)),by=2))]

#Cleanup
rm(AllTrends,TrendsFiles)

#Just in case we want this alone
save(JustTrends,file="JustTrends")
```

On to the forecast data.
```{r}

Loads<- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-hourly-loads.csv")

Forecasts <- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-rto-forecasts.csv")
```

There are a few columns we don't need so trim and we need some dates in ISO format
```{r}
Loads<-Loads[,1:26]

# Date manipulation

Loads$Date<-as.POSIXct(Loads$DATE, format="%m/%d/%Y")
Forecasts$ForecastDate<-as.POSIXct(Forecasts$Effective., format="%m/%d/%Y")

#There are several forecasts in a day.  Use only the early one  5am
Forecasts<-Forecasts[as.POSIXlt(Forecasts$Evaluated.at.,format="%m/%d/%Y %H:%M:%S" )$hour==5,]

#Fix the date forecast was made on
Forecasts$Forecasted<-as.POSIXct(Forecasts$Evaluated.at.,format="%m/%d/%Y")

#Make sure we only have day ahead forecasts
table(Forecasts$Forecasted-Forecasts$ForecastDate)
Forecasts<-Forecasts[Forecasts$Forecasted-Forecasts$ForecastDate<0,]

```

Time to join the two tables.  The key will be to link them by the trends data from the day before the forecast.

```{r}
#Link forecasts to actual.

library(sqldf)

```

### 2014-07-24 DataManipulation/DataManipulation.Rmd
Recreated the proof of concept with hour 19 and checked the other trends ideas.

@@
 
-library(sqldf)
+#need to kill a few columns with . in the name
+Forecasts$Evaluated.at.<-NULL
+Forecasts$Effective.<-NULL
+names(Forecasts)[1:24]<-c("F01","F02","F03","F04","F05","F06","F07","F08","F09","F10","F11","F12","F13","F14","F15","F16","F17","F18","F19","F20","F21","F22","F23","F24")
+Forecasts$Date<-Forecasts$ForecastDate
+
+library(plyr)
+RTO<-join(Forecasts, Loads, by="Date")
+
+#clean up
+rm(Forecasts,Loads)
+
+#
+JustTrends$TrendDate<-JustTrends$Date
+JustTrends$Date<-as.POSIXct(JustTrends$Date)+2*60*24*60
+
+WTrends<-join(RTO,JustTrends, by="Date")
+#save for later use
+save(WTrends,file="WTrends")
 
 ```
+
+Summary
+```{r}
+summary(WTrends)
+
+```

### 2014-07-24 ResearchNotes/ResearchNotes.Rmd
Recreated the proof of concept with hour 19 and checked the other trends ideas.

---
title: "ResearchNotes"
author: "James Woods"
date: "07/24/2014"
output: html_document
---
Read in the data file created by the data manipulation

```{r}
load("~/Research/Forecast-Peak-With-Google-Trends/DataManipulation/WTrends")
```

Replicate the hour 19 experiment from the proof of concept.  First how well do the forecasts work.
```{r}
summary(lm(HE19~F19,data=WTrends))

```
Looks like they are a little high most of the times by 3,400 MW but they comove the right way.

Now to add just PA
```{r}
summary(lm(HE19~F19+PATrends,data=WTrends))

```
Try with something else

```{r}
summary(lm(HE19~F19+NewsTrends,data=WTrends))

```
Oh, that works too

```{r}
summary(lm(HE19~F19+GasTrends,data=WTrends))

```
Gas does not

```{r}
summary(lm(HE19~F19+TrafficTrends,data=WTrends))

```
Traffic does not
```{r}
summary(lm(HE19~F19+RestaurantTrends,data=WTrends))

```
Restaurant does not
```{r}
summary(lm(HE19~F19+MovieTrends,data=WTrends))

```
Snort...Movie does.  Cool place to be.

]

### 2014-07-25 ResearchNotes/ResearchNotes.Rmd
Formed the hourly models.  Wow those day ahead forecasts are terrible.  Working on the raw comparisions with model comparisions.

@@
 
-]
+Lets just check a few other hours
+
+```{r}
+summary(lm(HE11~F11+PATrends,data=WTrends))
+
+```
+
+```{r}
+summary(lm(HE05~F05+PATrends,data=WTrends))
+
+```
+Small in absolute terms
+
+# Weighting the search terms
+
+I need to weight the state weather search terms by population.
+These population estimates are from  "Annual Estimates of the Resident Population for the United States, Regions, States, and Puerto Rico: April 1, 2010 to July 1, 2013" (CSV).
+2013 Population Estimates.
+United States Census Bureau, Population Division.
+December 30, 2013.
+Retrieved December 30, 2013.
+
+Here is where it gets strange.  I can't get count, just an index normalized by state.  This then is a population weighted value of indexes and not a population weighted index.
+
+```{r}
+# DE 925,749
+# Maryland  5,928,814	
+# New Jersey  8,899,339	
+# Ohio  11,570,808
+# Pennsylvania  12,773,801
+# Virginia  8,260,405
+# West Virginia  1,854,304
+# Kentucky  4,395,295
+
+WTrends$Weather<-((925749*WTrends$DETrends)+(4395295*WTrends$KYTrends)+(5928814*WTrends$MDTrends)+(8899339*WTrends$NJTrends)+(11570808*WTrends$OHTrends)+(12773801*WTrends$PATrends)+(8260405*WTrends$VATrends)+(1854304*WTrends$WVTrends))/(925749+4395295+5928814+8899339+11570808+12773801+8260405+1854304)
+
+summary(WTrends$Weather)
+
+```
+Note that the index is now attenuated.
+
+# Model all hours
+```{r}
+
+HourModel<-function(hour){
+  Hour<-formatC(hour, width=2, flag="0")
+  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}
+
+lapply(1:24, FUN = function(x)  summary(lm(HourModel(x), data=WTrends)))
+
+```
+
+Quick summary is that google trends is helpful in all hours of the day. It also looks like the forecasts are usually off by a large amount.  I should look at those individually.
+
+```{r}
+
+HourModelForecastCheck<-function(hour){
+  Hour<-formatC(hour, width=2, flag="0")
+  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}
+
+lapply(1:24, FUN = function(x)  summary(lm(HourModelForecastCheck(x), data=WTrends)))
+
+```
+The intercept terms are almost all negative and almost all significant.  That means that they are forecasting high consistently.
+
+Checking if the forecasts comove well, i.e., confidence interval contains 1.
+
+```{r}
+
+HourModelForecastCheck<-function(hour){
+  Hour<-formatC(hour, width=2, flag="0")
+  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}
+
+lapply(1:24, FUN = function(x)  confint(lm(HourModelForecastCheck(x), data=WTrends)))
+
+```
+
+Looks like it comoves well during peak hours but over corrects, greater than 1 in the other hours.

### 2014-07-25 ResearchNotes/ResearchNotes.Rmd
Just showed with the full models that there are 6% improvments vs statistically adjusted forecasts and 60% vs the raw forecast errors.  I get the feeling that that forecasts mean something different than I think.  That is just not right.

@@
 
-Quick summary is that google trends is helpful in all hours of the day. It also looks like the forecasts are usually off by a large amount.  I should look at those individually.
+Quick summary is that Google trends is helpful in all hours of the day. It also looks like the forecasts are usually off by a large amount.  I should look at those individually.
 
@@
 Looks like it comoves well during peak hours but over corrects, greater than 1 in the other hours.
+
+Given this I need to compare not just the difference between actual and forecast but the difference between with trends data and statistically adjusted forecast.  It is just not fair.
+
+I will compare with the full model and via drop forward cross validation.
+
+#Compare sigma on three models
+
+For these comparisons I have to make sure I am using equal sized datasets.  So only those with trend data.
+
+```{r}
+WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]
+```
+
+Now create a function that compares the sigma of the two models.  I will call the one without Google trends data the statistically adjusted forecasts.
+
+```{r}
+
+# Gives percent reduction in sigma
+CompareSigma<-function(x){
+SA<-summary(lm(HourModelForecastCheck(x), data=WTrendsLimited))$sigma  
+Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma
+
+(SA-Google)/(SA)
+}
+
+lapply(1:24, FUN = CompareSigma)
+mean(unlist(lapply(1:24, FUN = CompareSigma)))
+
+```
+
+Nice percent savings vs the statistically adjusted model -- about 6% reduction average by hour.
+
+Now make a comparison to raw
+
+```{r}
+
+# Gives percent reduction in sigma
+CompareRaw<-function(x){
+SA<-sd(WTrendsLimited[,x]-WTrendsLimited[,30])  
+Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma
+
+(SA-Google)/(SA)
+}
+
+lapply(1:24, FUN = CompareRaw)
+mean(unlist(lapply(1:24, FUN = CompareRaw)))
+
+```
+Man that is huge.  Damn huge.  I must be misunderstanding what they mean by forecast.
+
+Time, to look at this from a drop forward point of view.
+
+# Compare with drop forward crossvalidation
+
+This will be a fairer comparison.  I will boot up each model with 15 observations that then look at how they predict the next day, updating the model each day.

### 2014-07-25 ResearchNotes/ResearchNotes.Rmd
Drop forward CV is done.  It works.  Need to write the paper now.

@@
 
-This will be a fairer comparison.  I will boot up each model with 15 observations that then look at how they predict the next day, updating the model each day.
+This will be a fairer comparison.  I will boot up each model with 20 observations that then look at how they predict the next day, updating the model each day.
+
+```{r}
+
+OneForwardError<-function(formula, nData){
+  model<-lm(formula, data=WTrendsLimited[1:nData,], y=TRUE)
+  modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
+  predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
+}
+
+CVDropForward<-function(model){sd(unlist(lapply(20:(length(WTrendsLimited)-1), FUN= function(x) OneForwardError(model,x))))}
+
+# CVDropForward(HourModel(1))
+
+```
+
+Lets look at the percent change in drop forward cross validation from the google trends with statistically adjusted model
+
+```{r}
+
+CompareSigmaCV<-function(x){
+SA<-CVDropForward(HourModelForecastCheck(x))  
+Google<-CVDropForward(HourModel(x))
+
+(SA-Google)/(SA)
+}
+
+CVImprove<-lapply(1:24, FUN = CompareSigmaCV)
+CVImprove
+mean(unlist(CVImprove))
+```
+I think the case for 5% is made. The case against their forecasts is very strong anyway.

### 2014-07-28 Paper/DraftPaper.Rnw
Added draft paper with outline and blank bib file.

\documentclass{article}

\usepackage{longtable}
\usepackage[margin=1in]{geometry}
\usepackage[section]{placeins}
\usepackage{cite}

\title{Improving Day Ahead Electricity Load Forecasts with Google Trends}
\author{Cameron Mulder\\ James Woods}

% \date{}

\begin{document}
\maketitle
\setkeys{Gin}{width=0.7\textwidth}

\begin{abstract}

\end{abstract}

\SweaveOpts{concordance=TRUE}

\section{Introduction}

<<echo=FALSE,results=hide>>=
load("~/Research/Forecast-Peak-With-Google-Trends/DataManipulation/WTrends")
@

\begin{enumerate}
  \item Intro to short term load forecasting.
  \item Why crowd sourced, non technical,  information could be useful.
  \item Google trends is the summation of Google searches.
  \item Outline of paper
\end{enumerate}

\section{Data Sources}

  \subsection{PJM Load Forecasts and Actuals}

    \begin{enumerate}
      \item Data sources.
      \item Documentation of forecasting.
      \item Forecast bias
      \item Statistically adjusted forecasts.
      \item Note that almost all hours are biased and that co-movements are good for peak hours
    \end{enumerate}

  \subsection{Google Trends}

    \begin{enumerate}
      \item Where to get the data
      \item Limitations
      \item Forming a population weighted index.
      \item Other common searches that will be used as counter examples.
    \end{enumerate}

\section{Post Forecast Addition of Google Trends Data}

  \begin{enumerate}
    \item Simple hourly models with Trends.
    \item Gross comparison with actual forecast and statistically adjusted forecasts.
    \item Why this is insufficient.
  \end{enumerate}

  \subsection{Drop Forward Cross-validation}

    \begin{enumerate}
      \item Cross validation concepts.
      \item Why drop forward cross validation is the right concept.
      \item Comparison of drop forward statistically adjusted and Trends adjusted with gross comparisons.
      \item Reiteration that comparison with raw forecasts is a slam dunk.
    \end{enumerate}

  \subsection{Counter-factual Test with Other Common Google Searches}
    \begin{enumerate}
      \item Comparison with: news, recipe, traffic, gas.
      \item Note that some of them kinda work.
    \end{enumerate}

\section{Summary and Conclusions}

% \bibliography{Trends.bib}
% \bibliographystyle{apalike}

\end{document}

### 2014-07-28 Paper/DraftPaper.Rnw
Abstract added.

@@
 \begin{abstract}
-
+Modern short term load forecasting has grown in analytically complexity and sophistication.
+Day ahead forecasts now commonly use neural nets, Monte Carlo simulations and a wealth of historical data.
+What they have not done is fully captured the sentiment and intentions of the people using the electricity.
+This paper introduces Google Trend data, a summary of Google searches, as a way of capturing this sentiment and refining forecasts.
+We show with drop all forward cross validation that this amendment decreases forecast uncertainty by approximately 5\% when compared to a statistically adjusted forecast and by over 50\% when compared to raw forecasts.
 \end{abstract}

### 2014-07-28 Paper/DraftPaper.Rnw
Added all the needed calculations from ResearchNotes.Rmd

@@
 load("~/Research/Forecast-Peak-With-Google-Trends/DataManipulation/WTrends")
+
+WTrends$Weather<-((925749*WTrends$DETrends)+(4395295*WTrends$KYTrends)+(5928814*WTrends$MDTrends)+(8899339*WTrends$NJTrends)+(11570808*WTrends$OHTrends)+(12773801*WTrends$PATrends)+(8260405*WTrends$VATrends)+(1854304*WTrends$WVTrends))/(925749+4395295+5928814+8899339+11570808+12773801+8260405+1854304)
 @
@@
   \subsection{PJM Load Forecasts and Actuals}
+<<>>=
+HourModelForecastCheck<-function(hour){
+  Hour<-formatC(hour, width=2, flag="0")
+  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}
+
+SAResults<-lapply(1:24, FUN = function(x)  lm(HourModelForecastCheck(x), data=WTrends))
+
+@
 
@@
 
+<<echo=false,results=hide>>=
+WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]
+
+HourModel<-function(hour){
+  Hour<-formatC(hour, width=2, flag="0")
+  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}
+
+# Gives percent reduction in sigma
+CompareRaw<-function(x){
+SA<-sd(WTrendsLimited[,x]-WTrendsLimited[,30])  
+Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma
+
+(SA-Google)/(SA)
+}
+
+lapply(1:24, FUN = CompareRaw)
+mean(unlist(lapply(1:24, FUN = CompareRaw)))
+
+@
+
+<<echo=false,results=hide>>=
+HourModel<-function(hour){
+  Hour<-formatC(hour, width=2, flag="0")
+  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}
+
+GrossTrends<-lapply(1:24, FUN = function(x)  lm(HourModel(x), data=WTrends))
+@
+
+<<echo=false,results=hide>>=
+
+# Gives percent reduction in sigma
+CompareSigma<-function(x){
+SA<-summary(lm(HourModelForecastCheck(x), data=WTrendsLimited))$sigma  
+Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma
+
+(SA-Google)/(SA)
+}
+
+lapply(1:24, FUN = CompareSigma)
+mean(unlist(lapply(1:24, FUN = CompareSigma)))
+
+@
+
   \subsection{Drop Forward Cross-validation}
+
+<<echo=false,results=hide>>=
+
+OneForwardError<-function(formula, nData){
+  model<-lm(formula, data=WTrendsLimited[1:nData,], y=TRUE)
+  modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
+  predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
+}
+
+CVDropForward<-function(model){sd(unlist(lapply(20:(length(WTrendsLimited)-1), FUN= function(x) OneForwardError(model,x))))}
+
+CompareSigmaCV<-function(x){
+SA<-CVDropForward(HourModelForecastCheck(x))  
+Google<-CVDropForward(HourModel(x))
+
+(SA-Google)/(SA)
+}
+
+CVImprove<-lapply(1:24, FUN = CompareSigmaCV)
+CVImprove
+mean(unlist(CVImprove))
+@
 
@@
   \subsection{Counter-factual Test with Other Common Google Searches}
+
     \begin{enumerate}
@@
     \end{enumerate}
+
+<<echo=false,results=hide>>=
+summary(lm(HE19~F19+NewsTrends,data=WTrends))
+# Oh, that works too
+summary(lm(HE19~F19+GasTrends,data=WTrends))
+# Gas does not
+summary(lm(HE19~F19+TrafficTrends,data=WTrends))
+# Traffic does not
+summary(lm(HE19~F19+RestaurantTrends,data=WTrends))
+# Restaurant does not
+summary(lm(HE19~F19+MovieTrends,data=WTrends))
+# Snort...Movie does.  Cool place to be.
+@
 

### 2014-07-29 Paper/DraftPaper.Rnw
graphics for statistically adjusted forecasts done.  BTW spotted an error in the hour two data.

@@
   \subsection{PJM Load Forecasts and Actuals}
+
 <<>>=
@@
 
+@
+
+\begin{figure}
+\begin{center}
+\caption{Confidence Intervals for Intercept (95\%)}
+<<echo=false,fig=TRUE>>=
+library(ggplot2)
+LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,1]))
+HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,2]))
+InterceptResults<-data.frame(1:24,LowInter,HighInter)
+names(InterceptResults)[1]<-"Hour"
+
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
+@
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\caption{Confidence Intervals for Co-Movement (95\%)}
+<<echo=false,fig=TRUE>>=
+library(ggplot2)
+LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,1]))
+HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,2]))
+InterceptResults<-data.frame(1:24,LowInter,HighInter)
+names(InterceptResults)[1]<-"Hour"
+
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
+@
+\end{center}
+\end{figure}
+
+<<>>=
+library(ggplot2)
+ggplot(WTrends)+
+geom_point(aes(F01,HE01,shape='a'))+geom_point(aes(F02,HE02,shape="b"))+
+geom_point(aes(F03,HE03,shape='c'))+geom_point(aes(F04,HE04,shape="d"))+
+geom_point(aes(F05,HE05,shape='e'))+geom_point(aes(F06,HE06,shape="f"))+
+geom_abline(intercept = 0, slope = 1)
 @

### 2014-07-29 Paper/DraftPaper.Rnw
Most of the tables and figure are in.  I may add one that shows that all the weather searches are significant.

--- 2014-07-28 Paper/DraftPaper.Rnw
@@
   \subsection{PJM Load Forecasts and Actuals}
-<<>>=
+
+<<echo=false,results=hide>>=
 HourModelForecastCheck<-function(hour){
@@
 @
+
+\begin{figure}
+\begin{center}
+\caption{Confidence Intervals for Intercept Statistically Adjusted Models (95\%)}
+<<echo=false,fig=TRUE>>=
+library(ggplot2)
+LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,1]))
+HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,2]))
+InterceptResults<-data.frame(1:24,LowInter,HighInter)
+names(InterceptResults)[1]<-"Hour"
+
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
+@
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\caption{Confidence Intervals for Co-Movement Statistically Adjusted Models (95\%)}
+<<echo=false,fig=TRUE>>=
+library(ggplot2)
+LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,1]))
+HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,2]))
+InterceptResults<-data.frame(1:24,LowInter,HighInter)
+names(InterceptResults)[1]<-"Hour"
+
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
+@
+\end{center}
+\end{figure}
 
@@
   \subsection{Google Trends}
+
+\begin{figure}
+\begin{center}
+\caption{State Weather Trends Indexes Over Time}
+<<echo=false,fig=TRUE>>=
+library(ggplot2)
+library(reshape2)
+
+JustWeather<-data.frame(WTrends$Date, WTrends$DETrends,WTrends$KYTrends, WTrends$MDTrends, WTrends$NJTrends, WTrends$OHTrends, WTrends$PATrends, WTrends$VATrends, WTrends$WVTrends, WTrends$Weather)
+
+names(JustWeather)<-c("Date","DE","KY","MD","NJ","OH","PA","VA","WV","Weather")
+
+MeltedTrends<-melt(JustWeather,variable.name="Index",id.var="Date",na.rm=TRUE)
+
+ggplot(MeltedTrends, aes(Date, value,group= Index))+geom_line() +ylab("Index")+facet_grid(Index~.)
+
+@
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\caption{Trends Indexes Over Time}
+<<echo=false,fig=TRUE>>=
+library(ggplot2)
+library(reshape2)
+
+JustTrends<-data.frame(WTrends$Date, WTrends$GasTrends,WTrends$MovieTrends, WTrends$NewsTrends, WTrends$RestaurantTrends, WTrends$TrafficTrends,WTrends$Weather)
+names(JustTrends)<-c("Date","Gas","Movie","News","Restaurant","Traffic","Weather")
+
+MeltedTrends<-melt(JustTrends,variable.name="Index",id.var="Date",na.rm=TRUE)
+
+ggplot(MeltedTrends, aes(Date, value,group= Index))+geom_line() +ylab("Index")+facet_grid(Index~.)
+
+@
+\end{center}
+\end{figure}
 
@@
 
-lapply(1:24, FUN = CompareRaw)
+DirectCompare<-lapply(1:24, FUN = CompareRaw)
 mean(unlist(lapply(1:24, FUN = CompareRaw)))
@@
 
-lapply(1:24, FUN = CompareSigma)
+ModelCompare<-lapply(1:24, FUN = CompareSigma)
 mean(unlist(lapply(1:24, FUN = CompareSigma)))
@@
 
+<<echo=FALSE,results=tex>>=
+ForCompareTable<-data.frame(1:24,unlist(DirectCompare)*100,unlist(ModelCompare)*100,unlist(CVImprove)*100)
+names(ForCompareTable)<-c("Hour","Direct","Statistically Adjusted (Raw)", "Statistically Adjusted (CV)")
+library(stargazer)
+stargazer(ForCompareTable,summary=FALSE, title="Improvement in Forecasts Relative to Gross,  Statistically Adjusted, Drop Forward CV (Percent)",rownames=FALSE)
+@
+
     \begin{enumerate}
@@
 
-<<echo=false,results=hide>>=
-summary(lm(HE19~F19+NewsTrends,data=WTrends))
+<<echo=false,results=tex>>=
+News<-lm(HE19~F19+NewsTrends,data=WTrends)
 # Oh, that works too
-summary(lm(HE19~F19+GasTrends,data=WTrends))
+Gas<-lm(HE19~F19+GasTrends,data=WTrends)
 # Gas does not
-summary(lm(HE19~F19+TrafficTrends,data=WTrends))
+Traffic<-lm(HE19~F19+TrafficTrends,data=WTrends)
 # Traffic does not
-summary(lm(HE19~F19+RestaurantTrends,data=WTrends))
+Restaurant<-lm(HE19~F19+RestaurantTrends,data=WTrends)
 # Restaurant does not
-summary(lm(HE19~F19+MovieTrends,data=WTrends))
+Movie<-lm(HE19~F19+MovieTrends,data=WTrends)
 # Snort...Movie does.  Cool place to be.
+library(stargazer)
+stargazer(News,Gas,Traffic,Restaurant,Movie,title="Alternate Google Search Models for Hour 19",column.labels=c("News","Gas","Traffic","Restaurant","Movie"), dep.var.caption="Hour 19 Load",dep.var.labels.include = FALSE)
 @
@@
 \section{Summary and Conclusions}
+
+\appendix
+
+\section{Hourly Models with Weather Searches}
+
+<<echo=false,results=tex>>=
+
+for(x in 1:12){
+  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
+}
+@
+\clearpage
+
+<<echo=false, results=tex>>=
+
+for(x in 13:24){
+  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
+}
+@
 

### 2014-07-29 Paper/DraftPaper.Rnw
Added figure that shows the google weather searches are significant for all hours.

@@
 
+\begin{figure}
+\begin{center}
+\caption{Confidence Intervals for ``Weather'' in Trends Models (95\%)}
+<<echo=false,fig=TRUE>>=
+library(ggplot2)
+
+LowInter<-unlist(lapply(GrossTrends, FUN= function(x) confint(x) [3,1]))
+HighInter<-unlist(lapply(GrossTrends, FUN= function(x) confint(x) [3,2]))
+InterceptResults<-data.frame(1:24,LowInter,HighInter)
+names(InterceptResults)[1]<-"Hour"
+
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Confidence Interval")
+@
+\end{center}
+\end{figure}
+
 <<echo=false,results=hide>>=
@@
 <<echo=false, results=tex>>=
-
 for(x in 13:24){

### 2014-07-30 Paper/DraftPaper.Rnw
Changed everything to AR(1).  This broke the stargazer reporting in appendix and drop all forward forecasting is not quite drop all forward.  The last is the last of the current model.

@@
 
+#Get rid of the zero forecast in hour two
+WTrends$F02[WTrends$F02==0]<-NA
+
 WTrends$Weather<-((925749*WTrends$DETrends)+(4395295*WTrends$KYTrends)+(5928814*WTrends$MDTrends)+(8899339*WTrends$NJTrends)+(11570808*WTrends$OHTrends)+(12773801*WTrends$PATrends)+(8260405*WTrends$VATrends)+(1854304*WTrends$WVTrends))/(925749+4395295+5928814+8899339+11570808+12773801+8260405+1854304)
@@
 <<echo=false,results=hide>>=
+library(nlme)
 HourModelForecastCheck<-function(hour){
@@
 
-SAResults<-lapply(1:24, FUN = function(x)  lm(HourModelForecastCheck(x), data=WTrends))
+SAResults<-lapply(1:24, FUN = function(x)  gls(HourModelForecastCheck(x), data=WTrends,corAR1(form=~1),na.action=na.omit))
 
@@
 
-ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
 @
@@
 
-ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
 @
@@
 
-GrossTrends<-lapply(1:24, FUN = function(x)  lm(HourModel(x), data=WTrends))
+GrossTrends<-lapply(1:24, FUN = function(x)  gls(HourModel(x), data=WTrends,corAR1(form=~1),na.action=na.omit))
 @
@@
 
-ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Confidence Interval")
+ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Confidence Interval")
 @
@@
 OneForwardError<-function(formula, nData){
-  model<-lm(formula, data=WTrendsLimited[1:nData,], y=TRUE)
-  modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
-  predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
+  model<-gls(formula, data=WTrendsLimited[1:nData,],corAR1(form=~1),na.action=na.omit)
+#   modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
+#   predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
+
+tail(resid(model),1)
+
 }
@@
 <<echo=false,results=tex>>=
-News<-lm(HE19~F19+NewsTrends,data=WTrends)
+News<-gls(HE19~F19+NewsTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
 # Oh, that works too
-Gas<-lm(HE19~F19+GasTrends,data=WTrends)
+Gas<-gls(HE19~F19+GasTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
 # Gas does not
-Traffic<-lm(HE19~F19+TrafficTrends,data=WTrends)
+Traffic<-gls(HE19~F19+TrafficTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
 # Traffic does not
-Restaurant<-lm(HE19~F19+RestaurantTrends,data=WTrends)
+Restaurant<-gls(HE19~F19+RestaurantTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
 # Restaurant does not
-Movie<-lm(HE19~F19+MovieTrends,data=WTrends)
+Movie<-gls(HE19~F19+MovieTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
 # Snort...Movie does.  Cool place to be.
@@
 <<echo=false,results=tex>>=
-
-for(x in 1:12){
-  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
-}
+# 
+# for(x in 1:12){
+#   stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
+# }
 @
@@
 <<echo=false, results=tex>>=
-for(x in 13:24){
-  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
-}
+# for(x in 13:24){
+#   stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
+# }
 @

### 2014-07-30 debug.R

@@ -1,0 +1,31 @@
+
+
+
+OneForwardError<-function(form, nData){
+  modelForm<-as.formula(form)
+  model<-gls(modelForm, data=WTrendsLimited[1:nData,],na.action=na.omit,corAR1(form=~1))
+  predict(model,WTrendsLimited[1+nData,])-WTrendsLimited[1+nData,as.character(modelForm[2])]
+}
+
+CVDropForward<-function(model){sd(unlist(lapply(20:(length(WTrendsLimited)-1), FUN= function(x) OneForwardError(model,x))))}
+
+CompareSigmaCV<-function(x){
+  SA<-CVDropForward(HourModelForecastCheck(x))  
+  Google<-CVDropForward(HourModel(x))  
+  
+  (SA-Google)/(SA)
+}
+
+CVImprove<-lapply(1:24, FUN = CompareSigmaCV)
+CVImprove
+mean(unlist(CVImprove))
+
+OneForwardError(HourModel(2),23)
+HourModel(2)
+lhs<-as.character(HourModel(2)[2])
+WTrendsLimited[,lhs]
+
+gls(HourModel(2), data=WTrendsLimited[1:23,],corAR1(form=~1),na.action=na.omit)
+model<-gls(HourModel(2), data=WTrendsLimited[1:23,],corAR1(form=~1),na.action=na.omit)
+
+predict(model,WTrendsLimited[1+23,])-WTrendsLimited[1+23,as.character(HourModel(2)[2])]

### 2014-07-30 Paper/DraftPaper.Rnw
Fixed the appendix tables.  Had to hard wire it.  Don't know why.  Bib started.

@@
 <<echo=false,results=tex>>=
-# 
-# for(x in 1:12){
-#   stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
-# }
+
+stargazer(gls(HourModel(1), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",1), dep.var.labels=paste("Hour",1), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(2), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",2), dep.var.labels=paste("Hour",2), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(3), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",3), dep.var.labels=paste("Hour",3), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(4), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",4), dep.var.labels=paste("Hour",4), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(5), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",5), dep.var.labels=paste("Hour",5), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(6), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",6), dep.var.labels=paste("Hour",6), covariate.labels=c("Forecast","Weather","Constant") )
+@
+\clearpage
+
+<<echo=false,results=tex>>=
+stargazer(gls(HourModel(7), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",7), dep.var.labels=paste("Hour",7), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(8), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",8), dep.var.labels=paste("Hour",8), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(9), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",9), dep.var.labels=paste("Hour",9), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(10), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",10), dep.var.labels=paste("Hour",10), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(11), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",11), dep.var.labels=paste("Hour",11), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(12), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",12), dep.var.labels=paste("Hour",12), covariate.labels=c("Forecast","Weather","Constant") )
+
 @
@@
 <<echo=false, results=tex>>=
+
+stargazer(gls(HourModel(13), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",13), dep.var.labels=paste("Hour",13), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(14), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",14), dep.var.labels=paste("Hour",14), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(15), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",15), dep.var.labels=paste("Hour",15), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(16), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",16), dep.var.labels=paste("Hour",16), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(17), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",17), dep.var.labels=paste("Hour",17), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(18), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",18), dep.var.labels=paste("Hour",18), covariate.labels=c("Forecast","Weather","Constant") )
+@
+\clearpage
+
+<<echo=false, results=tex>>=
+
+stargazer(gls(HourModel(19), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",19), dep.var.labels=paste("Hour",19), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(20), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",20), dep.var.labels=paste("Hour",20), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(21), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",21), dep.var.labels=paste("Hour",21), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(22), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",22), dep.var.labels=paste("Hour",22), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(23), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",23), dep.var.labels=paste("Hour",23), covariate.labels=c("Forecast","Weather","Constant") )
+stargazer(gls(HourModel(24), data=WTrends,corAR1(form=~1),na.action=na.omit), title=paste("Hour",24), dep.var.labels=paste("Hour",24), covariate.labels=c("Forecast","Weather","Constant") )
+
 # for(x in 13:24){

### 2014-08-05 DataManipulation/DataManipulation.Rmd
Updated data with July and reran.  I could probably use another month of data.

@@
 TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData")
+#Removing the subdirectory
+TrendsFiles[-12]
 
 #all the trends in one data frame
-AllTrends<-as.data.frame(lapply(TrendsFiles,FUN=ReadTrends))
+AllTrends<-as.data.frame(lapply(TrendsFiles[-12],FUN=ReadTrends))
 
@@
 
-Loads<- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-hourly-loads.csv")
+Loads<- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-hourly-loads.csv",header = TRUE)
 
-Forecasts <- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-rto-forecasts.csv")
+Forecasts <- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-rto-forecasts.csv",header = TRUE)
 ```
@@
 table(Forecasts$Forecasted-Forecasts$ForecastDate)
-Forecasts<-Forecasts[Forecasts$Forecasted-Forecasts$ForecastDate<0,]
+Forecasts<-Forecasts[Forecasts$Forecasted-Forecasts$ForecastDate<(-82800) ,]
 

### 2014-08-15 Paper/DraftPaper.Rnw
Trying to get the new data in and working.

@@
 <<echo=false,results=hide>>=
+WTrends$Weekend<-weekdays(as.Date(WTrends$Date)) %in% c('Saturday','Sunday')
 WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]
@@
   Hour<-formatC(hour, width=2, flag="0")
-  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}
+  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather:Weekend",sep='' ))}
 

### 2014-09-16 DataManipulation/DataManipulation.Rmd
Added in the August data.

@@
 ---
+Load data is from http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-data.aspx
+
+Forecasts are from
+
+http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-forecasts.aspx
+
 Load in the Trends data.
 ```{r}
+# Data is from
+Load data is from http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-data.aspx
+
+Forecasts are from
+
+http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-forecasts.aspx
 
@@
 #Get the names of the trend files
-TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData")
-#Removing the subdirectory
-TrendsFiles[-12]
+TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData", pattern="*.W.csv",all.files= FALSE)
 
 #all the trends in one data frame
-AllTrends<-as.data.frame(lapply(TrendsFiles[-12],FUN=ReadTrends))
+AllTrends<-as.data.frame(lapply(TrendsFiles,FUN=ReadTrends))
 

### 2014-09-16 ResearchNotes/GetTrendsData.Rmd
Added in the August data.

--- 2014-07-23 ResearchNotes/GoogleTrendLinks.Rmd
@@
+---
+title: "GetTrendsData.Rmd"
+author: "James Woods"
+date: "09/11/2014"
+output: html_document
+---
 Google Trend Links
@@
 http://www.google.com/trends/explore#q=weather&geo=US-WV&date=today%203-m&cmpt=date
+
+http://www.google.com/trends/explore#q=gas&date=today%203-m&cmpt=q
+http://www.google.com/trends/explore#q=Movie&date=today%203-m&cmpt=q
+http://www.google.com/trends/explore#q=News&date=today%203-m&cmpt=q
+http://www.google.com/trends/explore#q=Restaurant&date=today%203-m&cmpt=q
+http://www.google.com/trends/explore#q=Traffic&date=today%203-m&cmpt=q

### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Read data and on the way to figuring out how to do the seven day lag.

Working with the Long Data and heading to an AR model
========================================================

Load in data
```{r}
load("~/Forecast-Peak-With-Google-Trends/LongWtrends.RData")
summary(LongWtrends)
```

Data handling
```{r}
LongWtrends$hour<-as.factor(LongWtrends$hour)

```

### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Created new dataframe with the lagged values.

@@
 
+#create a date only variable not date time
+LongWtrends$DateOnly<-as.Date(LongWtrends$Date)
+
+library(sqldf)
+
+#used to merge on the lagged values
+CopyLong<-LongWtrends
+
+LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly-7) and LongWtrends.hour=CopyLong.hour;   ")
+
 ```

### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Base AR model in place.  Checking for alternate structures

@@
 
+summary(LagFormData)
+
 ```
+
+First test regression for hour 19
+
+```{r}
+summary(lm(HE~F+LagHE+Weather+LagWeather,data=LagFormData[LagFormData$hour=='19',]   ))
+library(lmtest)
+
+dwtest(HE~F+LagHE+Weather+LagWeather,data=LagFormData[LagFormData$hour=='19',])
+
+```
+
+Looks nice.  Lets do AR
+```{r}
+library(nlme)
+summary(gls(HE~F+LagHE+Weather+LagWeather, data=LagFormData[LagFormData$hour=='19',],corAR1(form=~1),na.action=na.omit))
+```
+
+So the action goes away.  Lets assume AR structure is with previous hour and not previous day.  This will take a while to run.  There are a lot of parameters.
+```{r}
+summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
+```
+
+FULL WIN.  It works.

### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Results are in with both the by hour and by day within hour AR stucture.

@@
 
-So the action goes away.  Lets assume AR structure is with previous hour and not previous day.  This will take a while to run.  There are a lot of parameters.
+So the action goes away.  Lets assume AR structure is with previous previous day within hour.  This will take a while to run.  There are a lot of parameters.
+
 ```{r}
+LagFormData<-sqldf("select * from LagFormData order by hour, DateOnly;")
+
+summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
+```
+Sweet works except hours 1-5
+
+Now go by hour within day
+
+```{r}
+LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
 summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
@@
 
-FULL WIN.  It works.
+and the results are different.  Now we have to figure out which is right, or perhaps both.

### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Added line to load sqldf package

@@
 Working with the Long Data and heading to an AR model
-========================================================
-
+=======================================================
+library("sqldf")
 Load in data

### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Several itterations of the model but nothing that is satisfactory.  Will continue with specification

--- 2014-10-28 LongDataResearchNotes/ARModel.Rmd
@@
 
-LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly-7) and LongWtrends.hour=CopyLong.hour;   ")
+LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly+7) and LongWtrends.hour=CopyLong.hour;   ")
 
@@
 
-summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
+summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))$tTable
 ```
@@
 LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
-summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
+ARbyHour<-gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit)
+summary(ARbyHour)$tTable
 ```
 
-and the results are different.  Now we have to figure out which is right, or perhaps both.
+and the results are different.  Now we have to figure out which is right, or perhaps both.  The likelyhood suggests hour within day, i.e., the worse one.
+
+Lets get into the day of week effects and see if it is still there.  There was a Monday and Tuesday problem
+
+```{r}
+LagFormData$DOW<-as.factor(weekdays(LagFormData$DateOnly))
+LagFormData$DayType<-"MidWeek"
+LagFormData$DayType[LagFormData$DOW=="Monday"| LagFormData$DOW=="Tuesday"]<-"EarlyWeek"
+LagFormData$DayType[LagFormData$DOW=="Saturday"| LagFormData$DOW=="Sunday"]<-"Weekend"
+LagFormData$DayType<-as.factor(LagFormData$DayType)
+summary(LagFormData)
+
+LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
+ARbyHourDay<-gls(HE~-1+(hour+(F+LagHE+Weather+LagWeather):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
+summary(ARbyHourDay)$tTable
+# 
+# ARbyHourDay<-gls(HE~(hour+(F+LagHE+Weather+LagWeather):hour):weekdays(DateOnly), data=LagFormData,corAR1(form=~1),na.action=na.omit)
+# summary(ARbyHourDay)$tTable
+```
+
+Try without lag of forecast
+
+```{r}
+
+LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
+ARbyHourDayNoLagLoad<-gls(HE~-1+(hour+(F+Weather+LagWeather):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
+summary(ARbyHourDayNoLagLoad)$tTable
+
+```
+
+We think that lag of actual is in the forecast.
+
+No lag of actual but with lag forecast
+
+```{r}
+
+LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
+ARbyHourDayLagF<-gls(HE~-1+(hour+(F+Weather+LagWeather+LagF):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
+summary(ARbyHourDayLagF)$tTable
+
+```

### 2014-11-18 LongDataResearchNotes/ARModel.Rmd
Fixing the merge.
Should finalize the model.

--- 2014-10-28 LongDataResearchNotes/ARModel.Rmd
@@
 Working with the Long Data and heading to an AR model
-========================================================
+=======================================================
 
@@
 ```
+Lets stick with this model and call it an imperfect but informative way of adding intent to forecast models.

### 2014-12-04 LongDataResearchNotes/ARModel.Rmd
Adding the CA Trends data

--- 2014-10-28 LongDataResearchNotes/ARModel.Rmd
@@
 ```{r}
-load("~/Forecast-Peak-With-Google-Trends/LongWtrends.RData")
+load("~/Research/Forecast-Peak-With-Google-Trends/LongWtrends.RData")
 summary(LongWtrends)
@@
 
-LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly+7) and LongWtrends.hour=CopyLong.hour;   ")
+LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly-7) and LongWtrends.hour=CopyLong.hour;   ")
 
@@
 
-So the action goes away.  Lets assume AR structure is with previous previous day within hour.  This will take a while to run.  There are a lot of parameters.
-
+So the action goes away.  Lets assume AR structure is with previous hour and not previous day.  This will take a while to run.  There are a lot of parameters.
 ```{r}
-LagFormData<-sqldf("select * from LagFormData order by hour, DateOnly;")
-
-summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))$tTable
-```
-Sweet works except hours 1-5
-
-Now go by hour within day
-
-```{r}
-LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
-ARbyHour<-gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit)
-summary(ARbyHour)$tTable
+summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
 ```
 
-and the results are different.  Now we have to figure out which is right, or perhaps both.  The likelyhood suggests hour within day, i.e., the worse one.
-
-Lets get into the day of week effects and see if it is still there.  There was a Monday and Tuesday problem
-
-```{r}
-LagFormData$DOW<-as.factor(weekdays(LagFormData$DateOnly))
-LagFormData$DayType<-"MidWeek"
-LagFormData$DayType[LagFormData$DOW=="Monday"| LagFormData$DOW=="Tuesday"]<-"EarlyWeek"
-LagFormData$DayType[LagFormData$DOW=="Saturday"| LagFormData$DOW=="Sunday"]<-"Weekend"
-LagFormData$DayType<-as.factor(LagFormData$DayType)
-summary(LagFormData)
-
-LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
-ARbyHourDay<-gls(HE~-1+(hour+(F+LagHE+Weather+LagWeather):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
-summary(ARbyHourDay)$tTable
-# 
-# ARbyHourDay<-gls(HE~(hour+(F+LagHE+Weather+LagWeather):hour):weekdays(DateOnly), data=LagFormData,corAR1(form=~1),na.action=na.omit)
-# summary(ARbyHourDay)$tTable
-```
-
-Try without lag of forecast
-
-```{r}
-
-LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
-ARbyHourDayNoLagLoad<-gls(HE~-1+(hour+(F+Weather+LagWeather):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
-summary(ARbyHourDayNoLagLoad)$tTable
-
-```
-
-We think that lag of actual is in the forecast.
-
-No lag of actual but with lag forecast
-
-```{r}
-
-LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
-ARbyHourDayLagF<-gls(HE~-1+(hour+(F+Weather+LagWeather+LagF):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
-summary(ARbyHourDayLagF)$tTable
-
-```
+FULL WIN.  It works.

### 2014-12-04 Paper/DraftPaper.Rnw

--- 2014-07-30 Paper/DraftPaper.Rnw
@@
 This paper introduces Google Trend data, a summary of Google searches, as a way of capturing this sentiment and refining forecasts.
-We show with drop all forward cross validation that this amendment decreases forecast uncertainty by approximately 5\% when compared to a statistically adjusted forecast and by over 50\% when compared to raw forecasts.
+We show with drop all forward cross validation that this amendment decreases forecast uncertainty when compared to a statistically adjusted forecast in the PJM control area.
 \end{abstract}
@@
 
-<<echo=FALSE,results=hide>>=
-load("~/Research/Forecast-Peak-With-Google-Trends/DataManipulation/WTrends")
-
-#Get rid of the zero forecast in hour two
-WTrends$F02[WTrends$F02==0]<-NA
-
-WTrends$Weather<-((925749*WTrends$DETrends)+(4395295*WTrends$KYTrends)+(5928814*WTrends$MDTrends)+(8899339*WTrends$NJTrends)+(11570808*WTrends$OHTrends)+(12773801*WTrends$PATrends)+(8260405*WTrends$VATrends)+(1854304*WTrends$WVTrends))/(925749+4395295+5928814+8899339+11570808+12773801+8260405+1854304)
-@
-
 \begin{enumerate}
+  \item Why and the research question why it is important, i.e., ancilary services cost.
   \item Intro to short term load forecasting.
   \item Why crowd sourced, non technical,  information could be useful.
+  \item Other places where trends data has been useful.
   \item Google trends is the summation of Google searches.
@@
   \subsection{PJM Load Forecasts and Actuals}
-
-<<echo=false,results=hide>>=
-library(nlme)
-HourModelForecastCheck<-function(hour){
-  Hour<-formatC(hour, width=2, flag="0")
-  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}
-
-SAResults<-lapply(1:24, FUN = function(x)  gls(HourModelForecastCheck(x), data=WTrends,corAR1(form=~1),na.action=na.omit))
-
-@
-
-\begin{figure}
-\begin{center}
-\caption{Confidence Intervals for Intercept Statistically Adjusted Models (95\%)}
-<<echo=false,fig=TRUE>>=
-library(ggplot2)
-LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,1]))
-HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,2]))
-InterceptResults<-data.frame(1:24,LowInter,HighInter)
-names(InterceptResults)[1]<-"Hour"
-
-ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
-@
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\caption{Confidence Intervals for Co-Movement Statistically Adjusted Models (95\%)}
-<<echo=false,fig=TRUE>>=
-library(ggplot2)
-LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,1]))
-HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,2]))
-InterceptResults<-data.frame(1:24,LowInter,HighInter)
-names(InterceptResults)[1]<-"Hour"
-
-ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
-@
-\end{center}
-\end{figure}
 
@@
   \subsection{Google Trends}
-
-\begin{figure}
-\begin{center}
-\caption{State Weather Trends Indexes Over Time}
-<<echo=false,fig=TRUE>>=
-library(ggplot2)
-library(reshape2)
-
-JustWeather<-data.frame(WTrends$Date, WTrends$DETrends,WTrends$KYTrends, WTrends$MDTrends, WTrends$NJTrends, WTrends$OHTrends, WTrends$PATrends, WTrends$VATrends, WTrends$WVTrends, WTrends$Weather)
-
-names(JustWeather)<-c("Date","DE","KY","MD","NJ","OH","PA","VA","WV","Weather")
-
-MeltedTrends<-melt(JustWeather,variable.name="Index",id.var="Date",na.rm=TRUE)
-
-ggplot(MeltedTrends, aes(Date, value,group= Index))+geom_line() +ylab("Index")+facet_grid(Index~.)
-
-@
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\caption{Trends Indexes Over Time}
-<<echo=false,fig=TRUE>>=
-library(ggplot2)
-library(reshape2)
-
-JustTrends<-data.frame(WTrends$Date, WTrends$GasTrends,WTrends$MovieTrends, WTrends$NewsTrends, WTrends$RestaurantTrends, WTrends$TrafficTrends,WTrends$Weather)
-names(JustTrends)<-c("Date","Gas","Movie","News","Restaurant","Traffic","Weather")
-
-MeltedTrends<-melt(JustTrends,variable.name="Index",id.var="Date",na.rm=TRUE)
-
-ggplot(MeltedTrends, aes(Date, value,group= Index))+geom_line() +ylab("Index")+facet_grid(Index~.)
-
-@
-\end{center}
-\end{figure}
 
@@
 
-<<echo=false,results=hide>>=
-WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]
-
-HourModel<-function(hour){
-  Hour<-formatC(hour, width=2, flag="0")
-  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}
-
-# Gives percent reduction in sigma
-CompareRaw<-function(x){
-SA<-sd(WTrendsLimited[,x]-WTrendsLimited[,30])  
-Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma
-
-(SA-Google)/(SA)
-}
-
-DirectCompare<-lapply(1:24, FUN = CompareRaw)
-mean(unlist(lapply(1:24, FUN = CompareRaw)))
-
-@
-
-<<echo=false,results=hide>>=
-HourModel<-function(hour){
-  Hour<-formatC(hour, width=2, flag="0")
-  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}
-
-GrossTrends<-lapply(1:24, FUN = function(x)  gls(HourModel(x), data=WTrends,corAR1(form=~1),na.action=na.omit))
-@
-
-\begin{figure}
-\begin{center}
-\caption{Confidence Intervals for ``Weather'' in Trends Models (95\%)}
-<<echo=false,fig=TRUE>>=
-library(ggplot2)
-
-LowInter<-unlist(lapply(GrossTrends, FUN= function(x) confint(x) [3,1]))
-HighInter<-unlist(lapply(GrossTrends, FUN= function(x) confint(x) [3,2]))
-InterceptResults<-data.frame(1:24,LowInter,HighInter)
-names(InterceptResults)[1]<-"Hour"
-
-ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Confidence Interval")
-@
-\end{center}
-\end{figure}
-
-<<echo=false,results=hide>>=
-
-# Gives percent reduction in sigma
-CompareSigma<-function(x){
-SA<-summary(lm(HourModelForecastCheck(x), data=WTrendsLimited))$sigma  
-Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma
-
-(SA-Google)/(SA)
-}
-
-ModelCompare<-lapply(1:24, FUN = CompareSigma)
-mean(unlist(lapply(1:24, FUN = CompareSigma)))
-
-@
-
   \subsection{Drop Forward Cross-validation}
-
-<<echo=false,results=hide>>=
-
-OneForwardError<-function(formula, nData){
-  model<-gls(formula, data=WTrendsLimited[1:nData,],corAR1(form=~1),na.action=na.omit)
-#   modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
-#   predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
-
-tail(resid(model),1)
-
-}
-
-CVDropForward<-function(model){sd(unlist(lapply(20:(length(WTrendsLimited)-1), FUN= function(x) OneForwardError(model,x))))}
-
-CompareSigmaCV<-function(x){
-SA<-CVDropForward(HourModelForecastCheck(x))  
-Google<-CVDropForward(HourModel(x))
-
-(SA-Google)/(SA)
-}
-
-CVImprove<-lapply(1:24, FUN = CompareSigmaCV)
-CVImprove
-mean(unlist(CVImprove))
-@
-
-<<echo=FALSE,results=tex>>=
-ForCompareTable<-data.frame(1:24,unlist(DirectCompare)*100,unlist(ModelCompare)*100,unlist(CVImprove)*100)
-names(ForCompareTable)<-c("Hour","Direct","Statistically Adjusted (Raw)", "Statistically Adjusted (CV)")
-library(stargazer)
-stargazer(ForCompareTable,summary=FALSE, title="Improvement in Forecasts Relative to Gross,  Statistically Adjusted, Drop Forward CV (Percent)",rownames=FALSE)
-@
 
@@
 
-<<echo=false,results=tex>>=
-News<-gls(HE19~F19+NewsTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
-# Oh, that works too
-Gas<-gls(HE19~F19+GasTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
-# Gas does not
-Traffic<-gls(HE19~F19+TrafficTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
-# Traffic does not
-Restaurant<-gls(HE19~F19+RestaurantTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
-# Restaurant does not
-Movie<-gls(HE19~F19+MovieTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
-# Snort...Movie does.  Cool place to be.
-library(stargazer)
-stargazer(News,Gas,Traffic,Restaurant,Movie,title="Alternate Google Search Models for Hour 19",column.labels=c("News","Gas","Traffic","Restaurant","Movie"), dep.var.caption="Hour 19 Load",dep.var.labels.include = FALSE)
-@
-
 \section{Summary and Conclusions}
@@
 
-<<echo=false,results=tex>>=
-# 
-# for(x in 1:12){
-#   stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
-# }
-@
-\clearpage
-
-<<echo=false, results=tex>>=
-# for(x in 13:24){
-#   stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
-# }
-@
-
 % \bibliography{Trends.bib}

### 2014-12-15 CAData/CAISO/LoadData.Rmd
Loading in an processing data from the CAISO on 7 day ahead and actual ISO loads.

---
title: "PrepCAISOData"
author: "James Woods"
date: "12/15/2014"
output: html_document
---

Read in the data from the CAISO

```{r}
setwd("/home/woodsj/Research/Forecast-Peak-With-Google-Trends/CAData/CAISO")
# Get the files names
files <- list.files(pattern="*.csv")

# First apply read.csv, then rbind
CAISORaw<- do.call("rbind", lapply(files, function(x) read.csv(x, stringsAsFactors = FALSE)))

```
Editing of data types.  Remember that most everything gets imported as a string.

```{r}

CAISORaw$MARKET_RUN_ID<-as.factor(CAISORaw$MARKET_RUN_ID)
CAISORaw$TAC_AREA_NAME<-as.factor(CAISORaw$TAC_AREA_NAME)
CAISORaw$StartTimeGMT<-as.POSIXct(CAISORaw$INTERVALSTARTTIME_GMT)
```
Now trim off all but the full ISO area

```{r}
CAISOWorking<-CAISORaw[CAISORaw$TAC_AREA_NAME=='CA ISO-TAC',]
save(CAISOWorking,file="CAISOWorking.Rdata")
```

### 2014-12-17 CAData/CAISO/LoadData.Rmd
Seeing how the forecasts and actuals compare.

@@
 ```{r}
+OldWD<-getwd()
 setwd("/home/woodsj/Research/Forecast-Peak-With-Google-Trends/CAData/CAISO")
@@
 ```
+
+Now lets sort out how the 7day ahead market is related to the actual
+
+```{r}
+
+CAISOWorking$Hour<-as.factor(CAISOWorking$OPR_HR)
+#line up actual and 7day with the time in the line
+
+Forecast<-CAISOWorking[CAISOWorking$MARKET_RUN_ID=="7DA",]
+Actual<-CAISOWorking[CAISOWorking$MARKET_RUN_ID=="ACTUAL",]
+
+library(sqldf)
+sqldf("select * from Actual;")
+
+sqldf("select Actual.Hour, Actual.OPR_DT, Actual.MW as Actual, Forecast.MW as Forecast from Forecast, Actual where Actual.Hour=Forecast.Hour and Actual.OPR_DT=Forecast.OPR_DT;")
+
+table(CAISOWorking$INTERVALSTARTTIME_GMT)
+
+#line up acutal with 7day from seven days before.
+
+```

### 2014-12-17 CAData/CAISO/LoadData.Rmd
Need to go back and unique some things.

--- 2014-12-15 CAData/CAISO/LoadData.Rmd
@@
 ```{r}
-setwd("/home/woodsj/Research/Forecast-Peak-With-Google-Trends/CAData/CAISO")
+OldWD<-getwd()
+setwd("/home/woodsj/Forecast-Peak-With-Google-Trends/CAData/CAISO")
 # Get the files names
@@
 ```
+
+Now lets sort out how the 7day ahead market is related to the actual
+
+```{r}
+
+CAISOWorking$Hour<-as.factor(CAISOWorking$OPR_HR)
+CAISOWorking$Date<-as.Date(CAISOWorking$OPR_DT)
+#line up actual and 7day with the time in the line
+
+Forecast<-CAISOWorking[CAISOWorking$MARKET_RUN_ID=="7DA",]
+Actual<-CAISOWorking[CAISOWorking$MARKET_RUN_ID=="ACTUAL",]
+
+library(sqldf)
+
+Current<-sqldf("select Actual.Hour, Actual.Date, Actual.MW as Actual, Forecast.MW as Forecast from Forecast, Actual where Actual.Hour=Forecast.Hour and Actual.Date=Forecast.Date;")
+Lag<-sqldf("select Actual.Hour, Actual.Date, Actual.MW as Actual, Forecast.MW as Forecast from Forecast, Actual where Actual.Hour=Forecast.Hour and Actual.Date=(Forecast.Date+7);")
+
+summary(lm(Actual~Forecast*Hour,data=Current))
+summary(lm(Actual~Forecast*Hour,data=Lag))
+
+```
+Looks like they report what the 7day ahead forecast was rather than what it is.  In other words Jan 1 shows what they had forecasted seven days ago not what they expect on the 8th.
+
+Now lets deal with why there are different numbers on the match.  Here is a table of the number of observations in each day.
+
+```{r}
+table(table(Current$Date))
+
+```
+
+That is an interesting pattern.  Guessing there were dups.  Checking the Working and Raw
+
+```{r}
+table(table(CAISOWorking$OPR_DT))
+table(table(CAISORaw$OPR_DT))
+
+```
+Looks like we need a unique or something.
+
+```{r}
+table(table(unique(CAISOWorking)$OPR_DT))
+table(table(CAISOWorking$OPR_DT))
+
+table(table(CAISORaw$OPR_DT))
+table(table(unique(CAISORaw)$OPR_DT))
+
+```
+
+Decide to only use the days with 48 obs.
+
+```{r}
+
+```

### 2014-12-17 CAData/CAISO/LoadData.Rmd
Getting ready to add trends data.

@@
 
-summary(lm(Actual~Forecast*Hour,data=Current))
-summary(lm(Actual~Forecast*Hour,data=Lag))
+summary(lm(Actual~Forecast,data=Current))
+summary(lm(Actual~Forecast,data=Lag))
 
@@
 ```{r}
+GoodDays<-names(table(CAISOWorking$OPR_DT)  )[table(CAISOWorking$OPR_DT)==48]
+RevisedWorking<-CAISOWorking[is.element(CAISOWorking$OPR_DT,GoodDays),]
+table(table(RevisedWorking$OPR_DT))
 
+Forecast<-RevisedWorking[RevisedWorking$MARKET_RUN_ID=="7DA",]
+Actual<-RevisedWorking[RevisedWorking$MARKET_RUN_ID=="ACTUAL",]
+
+Current<-sqldf("select Actual.Hour, Actual.Date, Actual.MW as Actual, Forecast.MW as Forecast from Forecast, Actual where Actual.Hour=Forecast.Hour and Actual.Date=Forecast.Date;")
+save(Current,file="Current.Rdata")
 ```
+
+Now get the google trends data in and attached.

### 2014-12-23 CAData/CAISO/LoadData.Rmd
Data in and model made but counterfactuals work too.

@@
 Now get the google trends data in and attached.
+
+```{r}
+Trends<- read.csv("~/Forecast-Peak-With-Google-Trends/CAData/TrendsCAWeeklyEdited.csv")
+
+#Extract the end of week.
+library(stringr)
+Trends$EndDate<-as.Date(str_sub(Trends$Week,14))
+summary(Trends)
+
+```
+
+Now lets hook this to the load and forecast data.
+
+```{r}
+library(sqldf)
+Trends$LastDate<-Trends$EndDate+7
+
+WTrends<-sqldf("select Current.*, Trends.* from Current, Trends where Current.Date>Trends.EndDate and Current.Date<=Trends.LastDate;   ")
+
+summary(WTrends)
+```
+
+On to the modeling
+
+```{r}
+Base<-lm(Actual~Forecast,data=WTrends)
+summary(Base)
+
+WWeather<-lm(Actual~Forecast+weather,data=WTrends)
+summary(WWeather)
+
+anova(Base,WWeather)
+```
+
+Concept proved.
+
+Try counterfactuals
+
+```{r}
+summary(lm(Actual~Forecast+traffic,data=WTrends))
+
+summary(lm(Actual~Forecast+restaurants,data=WTrends))
+
+summary(lm(Actual~Forecast+gas,data=WTrends))
+
+summary(lm(Actual~Forecast+movies,data=WTrends))
+```
+Well that sucks.  All the counterfactuals work too.  Check F test
+
+```{r}
+
+anova(Base,lm(Actual~Forecast+traffic,data=WTrends))
+
+anova(Base,lm(Actual~Forecast+restaurants,data=WTrends))
+
+anova(Base,lm(Actual~Forecast+gas,data=WTrends))
+
+anova(Base,lm(Actual~Forecast+movies,data=WTrends))
+```
+Now that is an interesting puzzel.

### 2014-12-23 CAData/CAISO/LoadData.Rmd
Basic model in but there is an AR problem.

@@
 Now that is an interesting puzzel.
+
+```{r}
+library(lmtest)
+dwtest(Base)
+
+```
+There is autocorrelation
+
+```{r}
+dwtest(lm(Actual~Forecast+traffic,data=WTrends))
+
+dwtest(lm(Actual~Forecast+restaurants,data=WTrends))
+
+dwtest(lm(Actual~Forecast+gas,data=WTrends))
+
+dwtest(lm(Actual~Forecast+movies,data=WTrends))
+
+```
+
+Autocorreleation in everything.
+
+Moving to a lag formulation like in the day ahead model.
+Add the lags to dataset
+```{r}
+
+CopyWTrends<-WTrends
+library(sqldf)
+
+WLags<-sqldf("select WTrends.*, CopyWTrends.Actual as LActual, CopyWTrends.Forecast LForecast, CopyWTrends.weather as LWeather, CopyWTrends.traffic as LTraffic,CopyWTrends.gas as LGas, CopyWTrends.movies as LMovies from WTrends, CopyWTrends  where WTrends.Hour=CopyWTrends.Hour and WTrends.Date=(CopyWTrends.Date-7) ")
+
+summary(WLags)
+```
+
+```{r}
+
+Base<-lm(Actual~-1 +(LActual+weather+LWeather)*Hour, data=WLags)
+
+summary(Base)
+dwtest(Base)
+```
+
+Buahhahah  It works better for the peak hours.  There is still AR
+
+```{r}
+library(nlme)
+#ARbyHourDay<-gls(Actual~-1 +(LActual+weather+LWeather), data=WLags,corAR1(form=~1),na.action=na.omit)
+
+```
+Gona need a bigger boat.  3.9Gb.
